Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-06-27 outputs/paper/paper.qmd
Updating paper.qmd

Pollution data was collected from the Government of Canada's National Air Pollution Surveillance (NAPS) Program [website](https://data-donnees.ec.gc.ca/data/air/monitor/national-air-pollution-surveillance-naps-program/Data-Donnees/?lang=en). This website contains pollution data from 2002 to 2020. Each year contains a file with continuous data and integrated data. I will be using continuous data for each year. The continuous data contains annual summaries and hourly data as well. I will be looking at the means for each year in the annual summaries data. These summaries include the city (which is Toronto in our case), the pollutant (these include: NO, NO2, NOX, O3, CO, PM2.5, and SO2), as well as the levels of each pollutant for each month of the year.

@@

-   Average

-   StdDeviation

>>>>

Pollution data was collected from the Government of Canada's National Air Pollution Surveillance (NAPS) Program [website](https://data-donnees.ec.gc.ca/data/air/monitor/national-air-pollution-surveillance-naps-program/Data-Donnees/?lang=en). This website contains pollution data from 2002 to 2020. Each year contains a file with continuous data and integrated data. I will be using continuous data for each year. The continuous data contains annual summaries and hourly data. I will be looking at the hourly data for CO (Carbon Monoxide), NO (Nitric Oxide), NO2 (Nitrogen Dioxide) , O3 (Ozone), and SO2 (Sulfur Dioxide). This data includes the city (which is Toronto in our case), the levels of each pollutant for each hour of every day.

@@

-   Mean level of pollution each day
